On Secure Delegation of SampBQP with a Classical Client

### 2019-11-23 qpip.tex
Fix autoref shenanigans

TODO Do something about this
\begin{algorithm}
	\floatname{algorithm}{Protocol}
	\caption{Amplification with simple input}
	\label{AlgAmp1}
	\begin{algorithmic}[1]
		\State The prover sends $\poly(n)$ copies of...
		\State The verifier picks $m+n$ copies...
		\State The verifier runs Chernoff bound on...
		\If{number of accepted copies $\geq (\frac{1}{2}-\frac{\varepsilon}{2})n$}
			\State Measure time step...
			\State Output the...
		\Else
			\State Reject
		\EndIf
	\end{algorithmic}
\end{algorithm}
TODO what's $n$?

@@

\begin{theorem}
	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, conditioned on this acceptance, $\mathcal{F}$ has probability at least $1-\frac{p}{\delta}$ to accept each register of the output.
\end{theorem}
\begin{proof}
	Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+m}}$ with $w_i$ as weights.

>>>>

\floatname{algorithm}{Protocol}
TODO Do something about this
\begin{algorithm}
	\caption{Amplification with simple input}
	\label{AlgAmp1}
	\begin{algorithmic}[1]
		\State The prover sends $\poly(n)$ copies of...
		\State The verifier picks $m+n$ copies...
		\State The verifier runs Chernoff bound on...
		\If{number of accepted copies $\geq (\frac{1}{2}-\frac{\varepsilon}{2})n$}
			\State Measure time step...
			\State Output the...
		\Else
			\State Reject
		\EndIf
	\end{algorithmic}
\end{algorithm}
TODO what's $n$?

@@

\begin{theorem}
	When \hyperref[AlgAmp1]{Protocol~\ref*{AlgAmp1}} accepts an input with probability greater than $\delta$, conditioned on this acceptance, $\mathcal{F}$ has probability at least $1-\frac{p}{\delta}$ to accept each register of the output.
\end{theorem}
\begin{proof}
	Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+m}}$ with $w_i$ as weights.
